Can diffusion alone explain brain-wide distribution of CSF tracers within 24 hours?

### 2019-07-24 tex/rev1/paper.tex
more updates

\begin{figure}
\includegraphics[width=0.95\textwidth]{../Zoom-PatID.png} 
\caption{Shows the percentage change in T1 signal unit ratios from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis. The color bar was restricted to the range $(0,100)$. }
\label{fig2} 
\end{figure}
Figure~\ref{fig1} shows distribution of MRI-contrast%CSF tracer
, as a percentage change in T1 signal unit ratios, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before the contrast was injected. The observation points are distributed over 5 observations within 1-2 hours after injection, a single observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours. 
Figure~\ref{fig2} shows the region selected for our computations. 
The software Freesurfer \cite{Dale1999179, FischlLiuDale, spf2007, reuter:robreg10} was used to segment and align each of the observations, which made it possible to estimate voxelwise signal increase.

@@

The implementation of the gradient regularization required that the boundary was decomposed to avoid the boundary values being continuous over different subdomains. We decomposed the boundary as seen in Figure~\ref{markedboundaryvalues}, with the red and blue boundary adjacent to the CSF. We defined the red boundary $\partial \Omega_r$ and the blue boundary $\partial \Omega_b$ as Dirichlet boundaries, while the green and yellow were Neumann boundaries. The regularization parameter $\gamma$ was subsequentally to non-zero in Eq.~\ref{\label{EQ::objf}}. We initially tested gradient regularization with the same parameter $\gamma$ on both boundaries, but the different distribution of tracers on the boundaries made it difficult to find an adequate value. It was observed that the concentration in the lateral ventricles were more uniform than that in the SAS, so we defined $\gamma$ as
\begin{equation}
\gamma = \begin{cases}
0.01\tilde{\gamma}  \in &\partial \Omega_{b} \\ 
\tilde{\gamma} \qquad \in  &\partial \Omega_{r}
\end{cases}  
\end{equation} 
with $\tilde{\gamma}$ as the referenced, i.e. mentioned in the text, regularization parameter.

The projection method worked by selecting each boundary vertex on $\Omega_b$ and $\Omega_r$, then finding the corresponding voxel using an affine transformation. Then for each voxels, we  computed the average of all CSF segmented voxels in a two voxel vicinity. The averages was then set to be the observational value for corresponding boundary vertex in the computations.

We used the Gaussian smoothing found in the python-module scipy~\cite{jones2001scipy}, and applied the smoothing to the voxel based MRI-data. The smoothing function required that standard deviation of a Gaussian distribution was specified, which was tested in the range 0.3-1.5.

@@

\subsubsection{Results obtained when using real observations}
The MRI data consisted of the observations at times $t_i$ distributed in the 48 hours time frame with the time $t_i=0.00$ \lars{zero?} as the first observation 1-2 hours after the contrast was injected. There was no significant visible change in the contrast between the observations the first 2 hours, therefore we used observation times listed in Table ??.

The estimation of contrast concentration proved difficult in the CSF compartment. Therefore the 2 domain mesh, shown in Figure~\ref{Fig::Mesh} was used in the computation.

@@

%The MRI observations describes an influx of tracer into an empty compartment filled with an porous medium. In the static state, diffusion will be dominant 
\lars{Kent: artikkel av sharp,carara og bryn} 
Recently,   \cite{sharp2019dispersion} (Enhancement is 5.8 times that of molecular diffusion)

\lars{ Questions:
The fluctuations caused by shear-augmented dispersion is not detected by the DTI?  (why? is it?) }

>>>>

\begin{figure}
\includegraphics[width=0.95\textwidth]{../Zoom-PatID.png} 
\caption{The image shows the percentage change in T1 signal unit ratios from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis. The color bar was restricted to the range $(0,100)$. }
\label{fig2} 
\end{figure}
Figure~\ref{fig1} shows distribution of MRI-contrast%CSF tracer
, as a percentage change in T1 signal unit ratios, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before the contrast was injected. The observation points are distributed over 5 observations within 1-2 hours after injection, a single observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours. 
Figure~\ref{fig2} shows the region selected for our computations. 
The software Freesurfer \cite{Dale1999179, FischlLiuDale, spf2007, reuter:robreg10} was used to segment and align each of the observations, which made it possible to estimate voxelwise signal increase.

@@

The implementation of the gradient regularization required that the boundary was decomposed to avoid the boundary values being continuous over different subdomains. We decomposed the boundary as seen in Figure~\ref{markedboundaryvalues}, with the red and blue boundary adjacent to the CSF. We defined the red boundary $\partial \Omega_r$ and the blue boundary $\partial \Omega_b$ as Dirichlet boundaries, while the green and yellow were Neumann boundaries. The regularization parameter $\gamma$ was subsequently set to be non-zero in Eq.~\ref{EQ::objf}. We initially tested gradient regularization with the same parameter $\gamma$ on both boundaries, but the different distribution of tracers on the boundaries made it difficult to find an adequate value. It was observed that the concentration in the lateral ventricles were more uniform than that in the SAS, so we defined $\gamma$ as
\begin{equation}
\gamma = \begin{cases}
0.01\tilde{\gamma}  \in &\partial \Omega_{b} \\ 
\tilde{\gamma} \qquad \in  &\partial \Omega_{r}
\end{cases}  
\end{equation} 
with $\tilde{\gamma}$ as the referenced, i.e. mentioned in the text, regularization parameter.

The projection method worked by selecting each boundary vertex on $\Omega_b$ and $\Omega_r$, then finding the corresponding voxel using an affine transformation. Then for each voxels, we  computed the average of all CSF segmented voxels in a three voxel vicinity. The averages was then set to be the observational value for corresponding boundary vertex in the computations. In order to estimate the CSF concentration, we assumed that the T1 value corresponding to CSF was 3000 ms, which is shown in Fig~\ref{figureF}] in the supplementary.

We used the Gaussian smoothing found in the python-module scipy~\cite{jones2001scipy}, and applied the smoothing to all voxel based MRI observations. The smoothing function required that standard deviation of a Gaussian distribution was specified, which was tested in the range 0.3-1.5 mm, with 1.0 mm as length of a voxel.

@@

\subsubsection{Results obtained when using real observations}
The MRI data consisted of the observations at times $t_i$ distributed in the 48 hours time frame with the time $t_i=0.00$ as the first observation 1-2 hours after the contrast was injected. There was no significant visible change in the contrast between the observations the first 2 hours, therefore we used observation times listed in Table\ref{model-params-overview}.

%The estimation of contrast concentration proved difficult in the CSF compartment. Therefore the 2 domain mesh, shown in Figure~\ref{Fig::Mesh} was used in the computation.

@@

%The MRI observations describes an influx of tracer into an empty compartment filled with an porous medium. In the static state, diffusion will be dominant 
\lars{Kent: artikkel av sharp,carara og bryn} 
Recently, it was reported in \citet{sharp2019dispersion} that shear-augmented dispersion can contribute to an enhancement upto 5.8 times that of molecular diffusion.

%\lars{ Questions:
%The fluctuations caused by shear-augmented dispersion is not detected by the DTI?  (why? is it?) }

### 2019-07-24 tex/rev1/supplementary.tex
more updates

\begin{figure}
\centering
\includegraphics[scale=0.18]{../Convergence-plot.png}   
\caption{Convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
\label{convergence}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.21]{../boundary_control.png}  
\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$. The left panel shows the legend for the plot over time, together with the selection of points. The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$. The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.  }
\label{boundarycontrol}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.18]{../Convergence-plot.png}   
\caption{The images shows convergence plots of the diffusion coefficients, boundary conditions and functional with respect to different $\alpha$ and $\beta$ values. } 
\label{convergence}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.21]{../boundary_control.png}  
\caption{ The images displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$. The left panel shows the legend for the plot over time, together with the selection of points. The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$. The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$.  }
\label{boundarycontrol}
\end{figure}

### 2019-07-24 tex/rev1/supplementarynew.tex
more updates

\begin{figure}
\centering
\includegraphics[width=0.70\textwidth]{../T1function.png} 
\caption{Shows the  function defined in \eqref{scaledmagnetization} where the white region indicates $T_1$ values for white matter, the grey region indicates $T_1$ values for grey matter, the blue region indicates $T_1$ values for CSF.  }
\label{figureF} 
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.70\textwidth]{../T1function.png} 
\caption{The image shows the function defined in \eqref{scaledmagnetization} where the white region indicates $T_1$ values for white matter, the grey region indicates $T_1$ values for grey matter, the blue region indicates $T_1$ values for CSF.  }
\label{figureF} 
\end{figure}
